Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-06 paper/paper.tex
Improve description of DFDs, fix figure labels

 \label{fig:c-}
 \caption{Two \newC programs}
\end{figure}

@@

 \label{fig:not-c-}
 \caption{A C program to compute Fibonacci numbers.}
\end{figure}

@@

 \caption{Abstract synthesis refinement loop\label{fig:abstract-refinement}}
\end{figure}

@@

 \caption{Abstract refinement algorithm\label{fig:abstract-refinement-code}}
\end{figure}

@@

 \label{fig:bitvector-program}
 \caption{A tricky bitvector program}
\end{figure}

@@

\begin{tabular}{lllll}
 \verb|add a b| & \verb|sub a b| & \verb|mul a b| & \verb|div a b| & \verb|neg a|
\end{tabular}

@@

\begin{tabular}{llllll}
 \verb|and  a b| & \verb|or a b| & \verb|xor a b| & \verb|ashr a b| & \verb|lshr a b| & \verb|not  a|
\end{tabular}

@@

 \label{fig:l-language}
 \caption{The language $\mathcal{L}$}
\end{figure}

@@

 \label{fig:c-synthverif}
 \caption{The {\sc synth} and {\sc verif} formulae expressed as a \newC program}
\end{figure}

In order to determine the validity of the {\sc synth} formula, we can now
check the {\sc synth} program for safety.  The {\sc synth} program is a
\newC program, which means we can check its safety by invoking a bounded
model checker, such as {\sc cbmc}.  Since \newC is a fragment of C,
the {\sc synth} program can also be compiled executable using {\sc gcc}.
We can add a small piece of code which searches all possible
$\mathcal{L}$-programs and evaluates each on the current test vectors until
it finds one which is correct, just like a conventional superoptimiser,
and compile the whole thing down to an executable.  This leaves
us with a very simple explicit-state model checker which decides
safety for {\sc synth}.  We can run the explicit-state model checker
in parallel with {\sc cbmc} and take the answer of whichever happens
to terminate first, stopping the other process.  This procedure is
depicted for {\sc synth} in Fig.~\ref{fig:synth-dfd} and for
{\sc verif} in Fig.~\ref{fig:verif-dfd}.

@@

\label{fig:synth-dfd}
\caption{Schematic diagram of {\sc synth}}
\end{figure}

@@

\label{fig:verif-dfd}
\caption{Schematic diagram of {\sc verif}}
\end{figure}

@@

\label{fig:paramsflow}
 \caption{Decision tree for increasing parameters of $\mathcal{L}$.}
\end{figure}

@@

 \label{fig:2sum}
 \caption{2Sum}
\end{figure}

@@

\label{fig:results-table}
\caption{Times for synthesis of machine integer benchmarks from {\sc brahma} paper}
\end{figure}

\begin{figure}
 \includegraphics[width=\linewidth]{figures/brahma_kalashnikov.pdf}
 \label{fig:brahma-kalashnikov}
 \caption{Brahma runtimes vs. Kalashnikov}
\end{figure}

>>>>

 \caption{Two \newC programs}
  \label{fig:c-}

\end{figure}

@@

 \caption{A C program to compute Fibonacci numbers.}
  \label{fig:not-c-}

\end{figure}

@@

 \caption{Abstract synthesis refinement loop
 \label{fig:abstract-refinement}}
\end{figure}

@@

 \caption{Abstract refinement algorithm
 \label{fig:abstract-refinement-code}}
\end{figure}

@@

 \caption{A tricky bitvector program}
  \label{fig:bitvector-program}
\end{figure}

@@

\begin{tabular}{llll}
 \verb|add a b| & \verb|sub a b| & \verb|mul a b| & \verb|div a b| \\
 \verb|neg a| & & &
\end{tabular}

@@

\begin{tabular}{llll}
 \verb|and  a b| & \verb|or a b| & \verb|xor a b| & \verb|ashr a b| \\
 \verb|lshr a b| & \verb|not  a| & &
\end{tabular}

@@

 \caption{The language $\mathcal{L}$}
 \label{fig:l-language}

\end{figure}

@@

 \caption{The {\sc synth} and {\sc verif} formulae expressed as a \newC program}
 \label{fig:c-synthverif}
\end{figure}

In order to determine the validity of the {\sc synth} formula, we can now
check the {\sc synth} program for safety.  The {\sc synth} program is a
\newC program, which means we can check its safety by invoking a bounded
model checker, such as {\sc cbmc}.  Since \newC is a fragment of C,
the {\sc synth} program can also be compiled using {\sc gcc}.
We can add a small piece of code which enumerates each possible
$\mathcal{L}$-programs, then evaluates program on the current test vectors by
running {\sc synth}. If it finds a program which is correct, it emits
the program as a candidate, just like a conventional superoptimiser.
The combination of this enumeration function and {\sc synth} can be compiled
to an executable using {\sc gcc}.  This leaves
us with a very simple explicit-state model checker which decides
safety for {\sc synth}.  We can run the explicit-state model checker
in parallel with {\sc cbmc} and take the answer of whichever happens
to terminate first, stopping the other process.  This procedure is
depicted for {\sc synth} in Fig.~\ref{fig:synth-dfd} and for
{\sc verif} in Fig.~\ref{fig:verif-dfd}.

@@

\caption{Schematic diagram of {\sc synth}}
\label{fig:synth-dfd}
\end{figure}

@@

\caption{Schematic diagram of {\sc verif}}
\label{fig:verif-dfd}
\end{figure}

@@

 \caption{Decision tree for increasing parameters of $\mathcal{L}$.}
 \label{fig:paramsflow}

\end{figure}

@@

 \caption{2Sum}
  \label{fig:2sum}

\end{figure}

@@

\caption{Times for synthesis of machine integer benchmarks from {\sc brahma} paper}
\label{fig:results-table}

\end{figure}

\begin{figure}
 \includegraphics[width=\linewidth]{figures/brahma_kalashnikov.pdf}
 \caption{Brahma runtimes vs. Kalashnikov}
  \label{fig:brahma-kalashnikov}

\end{figure}
